Carbonate chemistry at Ny-Ålesund

### 2021-12-13 awipev-CO2.Rmd

#### plot
kk <- tidyr::pivot_longer(calib_spectro, cols = starts_with("E0"), names_to = "variable", values_to = "value")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
  facet_grid(variable ~ ., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

@@

>>>>

```{r seaFET pH calib sf_calib 9m, echo=FALSE, message= FALSE, warning=FALSE}
###
#creaate new dataframe and CALIB to take into consideration only seafet data at the same depth than spectro (9m)
##
####
d_all_calib_depth <- d_all%>%
  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf, depth_discrete,deployment_sf)%>%
  dplyr::filter(depth_discrete == 9)

calib_spectro_depth_9m <- sf_calib(calEint = d_all_calib_depth$voltINT, calEext = d_all_calib_depth$voltEXT, calpH = d_all_calib_depth$ph_s_sf_temp_insi, calT = d_all_calib_depth$temp_sf, calSal = d_all_calib_depth$sal_insitu_ctd_interp)
# put number of deployment 
calib_spectro_depth_9m$deployment_sf <- d_all_calib_depth$deployment_sf

# make the mean of E0 by period of deployement
calib_spectro_depth_9m <- group_by(calib_spectro_depth_9m, deployment_sf) %>%
  summarise(E0int25 = mean(E0int25, na.rm = TRUE),
            E0ext25 = mean(E0ext25, na.rm = TRUE) 
            )
names(calib_spectro_depth_9m) <- c("deployment_sf", "E0int25_sf_9m", "E0ext25_sf_9m")

# add E0 mean to seaFET data per deployment
d_all <-left_join(d_all, calib_spectro_depth_9m,by="deployment_sf" )
```

```{r seaFET pH plot sf_calib , echo=FALSE, message= FALSE, warning=FALSE}
#### plot
kk <- tidyr::pivot_longer(d_all, cols = starts_with("E0"), names_to = "variable", values_to = "value")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
  facet_grid(variable ~ ., scales="fixed") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)

kbl(calib_spectro)%>%
    kable_paper() %>% 
    kable_styling(fixed_thead = T)
kbl(calib_spectro_depth_9m)%>%
    kable_paper() %>% 
    kable_styling(fixed_thead = T)

@@

```{r seaFET pH calculation sf_calc 9m, echo=FALSE, message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib_9m <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf_9m,  E0ext25 = d_all$E0ext25_sf_9m, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)

# bind new calibrated pH data to the seafet data set.
names(seafet_calib_9m) <- c("pHint_tot_sf_calib9m", "pHext_tot_sf_calib9m")
##########  Despike() ###########
d_all <- d_all %>%   
  dplyr::mutate(pHint_tot_sf_calib9m = oce::despike(seafet_calib_9m$pHint_tot_sf_calib9m, reference= "median", n=1, k=5001, replace="NA"),
                pHextt_tot_sf_calib9m = oce::despike(seafet_calib_9m$pHextt_tot_sf_calib9m, reference= "median", n=1, k=5001, replace="NA")
  )

d_all <- d_all %>%
  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
  dplyr::mutate(pHint_tot_sf_calib9m = seafet_calib_9m$pHint_tot_sf_calib9m)

seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_9m, pHint_tot_sf_calib9m)
seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
      dySeries("pHint_tot_sf_calib9m", label = "pH calib 9m", color =  "black", strokeWidth = 0, pointSize = 2 ) %>%
dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
  dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%

dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyAxis("y2",valueRange = c(-3, 9)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= c("2017-08-10 00:00:00","2021-01-20 23:00:00"))
rm(seafet_depth_xts)
